Making Sequential Programs Deterministic

### 2019-03-27 design.tex
Fix LaTeX error

\subsection{Determinism checker specific rules for precision}\label{precision}
We annotated the \codieid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet$\uparrow$ boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet Sets}. We added the following rule shown in Figure~\ref{fig-precision-rules} to our checker to improve precision.
\begin{figure}
    \todo{linebreak}
    $\infer[\sc{\mathit{SET \ PRECISION}}]{\Gamma \vdash \mathit{z : Det}}{\Gamma \vdash \mathit{x} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{x} \ \beta_{x}\rangle, \mathit{y} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{y} \ \beta_{y}\rangle & \mathit{z = x.equals(y)} & \langle \kappa_{x} \ \beta_{x}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle & \langle \kappa_{y} \ \beta_{y}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle }$

>>>>

\subsection{Determinism checker specific rules for precision}\label{precision}
We annotated the \codeid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet$\uparrow$ boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet Sets}. We added the following rule shown in Figure~\ref{fig-precision-rules} to our checker to improve precision.
\begin{figure}
    \todo{linebreak}
    $\infer[\sc{\mathit{SET \ PRECISION}}]{\Gamma \vdash \mathit{z : Det}}{\Gamma \vdash \mathit{x} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{x} \ \beta_{x}\rangle, \mathit{y} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{y} \ \beta_{y}\rangle & \mathit{z = x.equals(y)} & \langle \kappa_{x} \ \beta_{x}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle & \langle \kappa_{y} \ \beta_{y}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle }$
